\documentclass[margin, 10pt]{res} 

\usepackage{helvet} 

\setlength{\textwidth}{5.1in} 

\begin{document}


\moveleft.5\hoffset\centerline{\large\bf Anthony James Martinez} 
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip 
 
\moveleft.5\hoffset\centerline{3614 Bellevue Ave} 
\moveleft.5\hoffset\centerline{Los Angeles, California 90026}
\moveleft.5\hoffset\centerline{github.com/Anthony1234567}
\moveleft.5\hoffset\centerline{1234567anthony1234567@gmail.com}
\moveleft.5\hoffset\centerline{(323) 740-2305}

\begin{resume}
 
\section{OBJECTIVE}  

An internship or full-time position in the field of computers with special interests in applications programming, information processing, and alogithm design. 

\section{EDUCATION}

{\sl Bachelor of Science,} Mathematics \\
University of California Riverside, Riverside, CA, expected June 2016 \\
Concentration: Computational Mathematics \\
Minor: Statistics \\
GPA: 3.215


\section{COMPUTER \\ SKILLS} 

{\sl Languages \& Software:} 
C, C++, Python, Matlab, Octave, LaTeX, Office, Adobe acrobat \\
{\sl Operating Systems:} Linux, Unix, Windows, OSX \\
{\sl Version Control:} Git

\section{EXPERIENCE}

{\sl Math Undergraduate Research Group} \hfill Spring 2015 \\
Mathematics Department, University of California Riverside 

\begin{itemize} \itemsep -2pt 
\item Research in the field of data compression, focusing specifically on lossless data compression.
\item Wrote a program for which I implimented the Huffman algorithm to compress files and decompress already compressed files.
\item Gave a presentation of our findings to the math department.
\end{itemize}

\section{PROJECTS}

{\sl rshell} \\
Implimented a basic command shell that emulates the Bash shell for unix-based systems. Runs commands including a custom ls command, supports piping and input/output redirection, and handles various signals. 

{\sl Huffman\_Coder} \\
Program for which I implimented the Huffman algorithm for lossless data compression. Reduces the size of a file by getting rid of the redundancy in the file using short codewords to represent more frequent strings of bits and longer codewords to represent those that occur less often. This process is reversed to get back the original file.

\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

Member {\it The National Society of Collegiate Scholars}, UC Riverside \\
Member {\it Math Club}, UC Riverside

\end{resume}
\end{document}